Lasso_RCI_Response

### 2024-04-29 Lasso_RCI_Response.Rmd
updated tables and figures!

RCI_df_anx2 <- Mothership_post |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_post |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

view(ANX_JT_smol)
```

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

@@

write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx

mean(Mothership_lasso_anx$CUXOS_post)
sd(Mothership_lasso_anx$CUXOS_post)
```

## Vector of variables to summarize
table1_vars_dep <- c(colnames(Mothership_lasso_dep)[-1:-2])
table1_vars_dep <- table1_vars_dep[1:27]

@@

@@

```{r}
# 
# Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)
# left_join()
# 
# ## Vector of variables to summarize
# table1_vars_gen <- c(colnames(Mothership_lasso_joined)[-1:-3])
# table1_vars_gen<- table1_vars_gen[1:27]
# 
# Mothership_lasso
# 
# ## lastly get the overal treatment breakdown
# table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
# table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
# table1_gen <-data.frame(table1_gen)
# write_csv(table1_gen,"~/Downloads/table1_gen.csv")
# table1_gen

@@

Scores_tab
```
Figure 1: 
```{r}
# t test scores for differences pre post, between and within groups. 
Pre_Post_t_Scores <- c("")

@@

#2. Differences between group differences for pre and post scores of anxiety and depression.
  #2.1 Pre scores of anxiety
     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
  #2.2 Post scores of anxiety
     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post)
     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post)
     round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
  #2.3 Pre scores of depression
     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
  #2.4 Post scores of depression
     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
     sd(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post)
     sd(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post)
     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
```
dataset visualizatoin
```{r}
# #install.packages("ggdist")
# library("ggdist")
# 
# Mothership_lasso |> 
#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
#     geom_boxplot() +
#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
#     geom_jitter(color="black", size=.6 , alpha=0.9) +
#     theme(
#       legend.position="none",
#       plot.title = element_text(size=11)
#     ) +
# #    ggtitle("Pre scores of depression severity") +
#     xlab("Depression Severity") +
#     ylim(0,80)
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x=Trauma_C)) +
#   geom_bar()
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x= Current_Dx)) +
#         geom_histogram() +
#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank()) 
#

@@

@@

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}
# RCI STUFF
# RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
# colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
# #anxiety 
# 
# RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
# # Depresssion
# RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
# # #Total
# # RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
# 
# RCI_table

# JT Table
JT_table <- data.frame(matrix(NA,nrow = 2,ncol = 3))
colnames(JT_table) = c("Varaibles","Responder","Non-Responder")
#anxiety

JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso_anx$Anxiety_Responder)))
# Depresssion
JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso_dep$Depression_Responder)))

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    #Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

```{r}
## min model
  glm_min_dep <-
            glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Some_College  + Married + White +
        Days_not_attended_1 + Mood_C +
        CUDOS_pre + CUXOS_pre + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial",
      )

@@

  tidy.summary.min.dep <- tidy(glm_min_dep)

# Coefficients
  coefs.min.dep <- abs(coef(glm_min_dep))

@@

write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
```
1se -
```{r}

@@

  tidy.summary.1se.dep <- tidy(glm_1se_dep)
  tidy.summary.1se.dep
# Coefficients
  coefs.1se.dep <- abs(coef(glm_1se_dep))

# Odds ratio
  OR.1se.dep <- exp(coef(glm_1se_dep))

# OR 95% CI
  CI.1se.dep <- data.frame(exp(confint(glm_1se_dep)))

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep$type = c("Depression")
FP.1se.dep
```

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Some_College + Married + 
        White +  Days_complete_1 +Days_not_attended_1 + 
        Anxiety_D + Trauma_D + Other + 
        Substance_C + CUXOS_pre + rdqPOST_coping + 
        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

write_csv(FP.min.anx, "~/Downloads/FP.min.anx")

```
1se -
```{r}

@@

FP_anx <- read_csv("~/Downloads/FP.min.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

#Change the names of variables
FP_anx$Variable = Anx_reg_coefs

@@

Anx_reg_coefs[1:10] <- c("Age","Some_College","Married", "White","Days_complete","Days_not_attended", "Anxiety_D", "Trauma_D","Other", "Substance_C")
FP_anx$Variable = Anx_reg_coefs

>>>>

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_lasso_1 |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

view(DEP_JT_smol)
```

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
  )
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

@@

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

@@

table1_tab_anx[,2:7] <- table1_tab_anx
table1_tab_anx[,1] <- rownames(table1_tab_anx)
colnames(table1_tab_anx) <- c("Variables",colnames(table1_tab_anx)[1:6])

table1_tab_anx

write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
```

```{r}
## Vector of variables to summarize
table1_vars_dep <- c(colnames(Mothership_lasso_dep)[-1:-2])
table1_vars_dep <- table1_vars_dep[1:27]

@@

table1_tab_dep[,2:7] <- table1_tab_dep
table1_tab_dep[,1] <- rownames(table1_tab_dep)
colnames(table1_tab_dep) <- c("Variables",colnames(table1_tab_dep)[1:6])

@@

Means and SDs of post scores
```{r}

mean(Mothership_lasso_anx$CUXOS_post)
sd(Mothership_lasso_anx$CUXOS_post)

mean(Mothership_lasso_dep$CUDOS_post)
sd(Mothership_lasso_dep$CUDOS_post)

@@

Scores_tab
```
## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression

Table 3
```{r}
# RCI_table

# JT Table
JT_table <- data.frame(matrix(NA,nrow = 3,ncol = 6))
colnames(JT_table) = c("Instrument","Responder","Non-Responder", "Mean Pre Score", "RCI","JT Criterion A")
#discriptor row

JT_table[1,] = c(NA,"n","n", "M (SD)",NA,NA)
summary(Mothership_lasso_anx$Anxiety_Responder)[[1]]

#Anxiety
JT_table[2,] = c("CUXOS", 
                 summary(Mothership_lasso_anx$Anxiety_Responder)[[1]],
                 summary(Mothership_lasso_anx$Anxiety_Responder)[[2]],
                 paste0(round(mean(Mothership_lasso_anx$CUXOS_pre),2), " (", 
                        round(sd(Mothership_lasso_anx$CUXOS_pre),2),")"),
                 13,
                 21)

summary(Mothership_lasso_anx$Anxiety_Responder)[2]

# Depresssion
JT_table[3,] = c("CUDOS", 
                 summary(Mothership_lasso_dep$Depression_Responder)[[1]],             
                 summary(Mothership_lasso_dep$Depression_Responder)[[2]],
                 paste0(round(mean(Mothership_lasso_dep$CUDOS_pre),2), " (", 
                        round(sd(Mothership_lasso_dep$CUDOS_pre),2),")"),
                 21,
                 17)

###table 4A
Between Group Differences of Anxiety at Pre and Post Timepoints by Anxiety Treatment Response
```{r}
#table set up
tab4 <- data.frame(matrix(NA,nrow = 5,ncol = 5))
colnames(tab4) = c("Instrument","Responder","Non-Responder", "Test Score", "Effect Size")
tab4[1,] = c(NA,"M (SD)", "M (SD)", "t", "d")

#anxiety

t.test_pre_anx  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
t.test_post_anx <- t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)

t.test_pre_dep  <- t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
t.test_post_dep <- t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)

##mean
t.test_pre_anx$estimate[[1]]

t.test_pre_anx$statistic[[1]]

#CUXOS PRE
tab4[2,] = c(
  "CUXOS Pre",
  #Responder
  paste0(round(t.test_pre_anx$estimate[[1]],2)," (",
         round(sd(subset(Mothership_lasso_anx,
                         Anxiety_Responder == "Responder")$CUXOS_pre),2),
         ")"),
  #non-responder
  paste0(round(t.test_pre_anx$estimate[[2]],2)," (",
         round(sd(subset(Mothership_lasso_anx,
                         Anxiety_Responder == "Non-Responder")$CUXOS_pre),2),
         ")"),
  #t-stat
  round(t.test_pre_anx$statistic[[1]],2),
  #effect size
  round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
    )

#CUXOS Post
tab4[3,] = c(
  "CUXOS Post",
  #Responder
  paste0(round(t.test_post_anx$estimate[[1]],2)," (",
         round(sd(subset(Mothership_lasso_anx,
                         Anxiety_Responder == "Responder")$CUXOS_post),2),
         ")"),
  #non-responder
  paste0(round(t.test_post_anx$estimate[[2]],2)," (",
         round(sd(subset(Mothership_lasso_anx,
                         Anxiety_Responder == "Non-Responder")$CUXOS_post),2),
         ")"),
  #t-stat
  round(t.test_post_anx$statistic[[1]],2),
  #effect size
  round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
    )

#CUDOS PRE
tab4[4,] = c(
  "CUDOS Pre",
  #Responder
  paste0(round(t.test_pre_dep$estimate[[1]],2)," (",
         round(sd(subset(Mothership_lasso_dep,
                         Depression_Responder == "Responder")$CUDOS_pre),2),
         ")"),
  #non-responder
  paste0(round(t.test_pre_dep$estimate[[2]],2)," (",
         round(sd(subset(Mothership_lasso_dep,
                         Depression_Responder == "Non-Responder")$CUDOS_pre),2),
         ")"),
  #t-stat
  round(t.test_pre_dep$statistic[[1]],2),
  #effect size
  round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
    )

#CUDOS Post
tab4[5,] = c(
  "CUDOS Post",
  #Responder
  paste0(round(t.test_post_dep$estimate[[1]],2)," (",
         round(sd(subset(Mothership_lasso_dep,
                         Depression_Responder == "Responder")$CUDOS_post),2),
         ")"),
  #non-responder
  paste0(round(t.test_post_dep$estimate[[2]],2)," (",
         round(sd(subset(Mothership_lasso_dep,
                         Depression_Responder == "Non-Responder")$CUDOS_post),2),
         ")"),
  #t-stat
  round(t.test_post_dep$statistic[[1]],2),
  #effect size
  round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
    )

tab4
```

```{r}
# t test scores for differences pre post, between and within groups. 
Pre_Post_t_Scores <- c("")

@@

#2. Differences between group differences for pre and post scores of anxiety and depression.
  #2.1 Pre scores of anxiety
     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
     round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
  #2.2 Post scores of anxiety
     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post)
     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post)
     round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
  #2.3 Pre scores of depression
     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
     round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
  #2.4 Post scores of depression
     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
     sd(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post)
     sd(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post)
     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)

  test1  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)

test1$estimate[[1]] #responder pre cuxos mean

ataset visualizatoin
```{r}
# #install.packages("ggdist")
# library("ggdist")
# 
# Mothership_lasso |> 
#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
#     geom_boxplot() +
#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
#     geom_jitter(color="black", size=.6 , alpha=0.9) +
#     theme(
#       legend.position="none",
#       plot.title = element_text(size=11)
#     ) +
# #    ggtitle("Pre scores of depression severity") +
#     xlab("Depression Severity") +
#     ylim(0,80)
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x=Trauma_C)) +
#   geom_bar()
# 
# Mothership_lasso|>
# ggplot( mapping=aes(x= Current_Dx)) +
#         geom_histogram() +
#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   theme(legend.title = element_blank()) 
#

@@

anx_prepost

@@

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

```{r}
# min model
glm_min_dep <-
          glm(
    #Outcome varaible
      Depression_Responder ~
    # predictors
      Age_1  + Some_College + Married + IPT_track_1 +
      Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
      Trauma_C + Substance_C +
      rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
    #data
      data = Vars_dep,
    # type of regression : logistic = binary / binomial
      family = "binomial",
    )

  # glm_min_dep <-
  #           glm(
  #     #Outcome varaible
  #       Depression_Responder ~
  #     # predictors
  #       Age_1  +
  #       Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
  #       BPD_Co_C + Current_Dx + CUXOS_pre+
  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
  #     #data
  #       data = Vars_dep,
  #     # type of regression : logistic = binary / binomial
  #       family = "binomial",
  #     )

install.packages("rempsyc")
library(rempsyc)
nice_table(tidy.summary.min.dep)

@@

  tidy.summary.min.dep <- tidy(glm_min_dep)
  tidy.summary.min.dep
# Coefficients
  coefs.min.dep <- abs(coef(glm_min_dep))

@@

write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
```
1se -
```{r}
tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs

@@

  tidy.summary.1se.dep <- tidy(glm_1se_dep)
  tidy.summary.1se.dep
# Coefficients
  coefs.1se.dep <- round(abs(coef(glm_1se_dep)),2)

# Odds ratio
  OR.1se.dep <- round(exp(coef(glm_1se_dep)),2)

# OR 95% CI
  CI.1se.dep <- round(data.frame(exp(confint(glm_1se_dep))),2)

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep$p.adjusted <- round(FP.1se.dep$p.adjusted,2)
FP.1se.dep$type = c("Depression")
FP.1se.dep
```

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Days_complete_1 + Days_not_attended_1 + Anxiety_C + Substance_C + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
```
1se -
```{r}
tmp_coeffs <- coef(lasso.model.1se.anx, s = "lambda.1se")
Anx_coefs2 <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Anx_reg_coefs2 <- Anx_coefs[2:length(Anx_coefs)]
Anx_reg_coefs2

@@

FP_anx <- read_csv("~/Downloads/FP.1se.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

#Change the names of variables
FP_anx$Variable = Anx_reg_coefs2

@@

# Anx_reg_coefs[1:8] <- c("Days completed","Days not attended", "Co-Anxiety",         "Co-Substance",        "Post coping" ,     "Post pmh"     ,   
# "Post functioning"   ,     "Post wellbeing" )
# FP_anx$Variable = Anx_reg_coefs
